Education and the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-14 GEMDataSource.Rmd
Cleaned document and added citations

# Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
library(repmis)
library(tidyr)
library(reshape2)
library(plyr)
library(WDI)
library(stargazer)

# Load citation package
pkgs <- c('repmis', 'tidyr', 'reshape2', 'plyr', 'WDI')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

>>>>

# Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)
library(stargazer)

# Load citation package
pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')
